Name matching through deep learning

### 2018-11-19 old/paper2018/evaluation.tex
figure format
figure hacking
fixing table ref

\begin{table}[ht]
\caption{Precision and Recall by loss functions}
\label{precision_recall}
\begin{center}
%{\scriptsize
\begin{tabular}{|l|l|r|r|r|}
\hline
Entities & Loss & Recall & \multicolumn{2}{|c|}{Precision} \\
 & & & @1 & All \\
\hline
\multirow{4}{*}{People} & Adapted & .81 & .81 & .63 \\
\cline{2-5}
& Triplet & .74 & .84 & .55 \\
\cline{2-5}
& Improved & .71 & .52 & .45 \\
\cline{2-5}
& Angular & .04 & .09 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & .74 & .73 & .66 \\
\cline{2-5}
& Triplet & .74 & .75 & .67 \\
\cline{2-5}
& Improved & .74 & .72 & .65 \\
\cline{2-5}
& Angular & .26 & .32 & .22 \\
\hline
\end{tabular} %}
\end{center}
\end{table}

\begin{table}[ht]
\caption{Distance estimates after training}
\label{distance}
\begin{center}
%{\scriptsize 
\begin{tabular}{|l|l|r|r|r|r|}
\hline
Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c|}{Neg} \\
& & Mean & Std & Mean & Std \\
\hline
\multirow{4}{*}{People} & Adapted & 1.59 & 4.05 & 2.44 & 2.45 \\
\cline{2-6}
& Triplet & .46 & .18 & .55 & .10 \\
\cline{2-6}
& Improved & .15 & .38 & .21 & .18 \\
\cline{2-6}
& Angular & .51 & .25 & .06 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & 2.39 & 3.62 & 3.59 & 2.72 \\
\cline{2-6}
& Triplet & .43 & .31 & .59 & .09 \\
\cline{2-6}
& Improved & .32 & .50 & .42 & .19 \\
\cline{2-6}
& Angular & .07 & .04 & .04 & .01 \\
\hline
\end{tabular}%}
\end{center}
\end{table}

@@

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Table \ref{distance}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.  For companies, it is from 16\% to 74\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.  Precision@1 improves from 10\% to 81\% for people and from 26\% to 75\% for companies.  In both these cases, demonstrable training occurred.

@@

\begin{table}[ht]
\caption{Precision and Recall for hard and semi-hard training}
\label{hard-semi-hard}
\begin{center}
%{\scriptsize
\begin{tabular}{|l|r|r|r|}
\hline
Training & Recall & Precision@1 & Precision \\
\hline
hard & .81 & .81 & .63 \\
\hline
semi-hard & .63 & .61 & .43 \\
\hline
\end{tabular}%}
\end{center}
\end{table}

>>>>

\begin{wrapfigure}{r}{.4\textwidth}
\subfloat[Precision and Recall by loss functions\label{precision_recall}]{%
{\scriptsize
\begin{tabular}{|l|l|r|r|r|}
\hline
Entities & Loss & Recall & \multicolumn{2}{|c|}{Precision} \\
 & & & @1 & All \\
\hline
\multirow{4}{*}{People} & Adapted & .81 & .81 & .63 \\
\cline{2-5}
& Triplet & .74 & .84 & .55 \\
\cline{2-5}
& Improved & .71 & .52 & .45 \\
\cline{2-5}
& Angular & .04 & .09 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & .74 & .73 & .66 \\
\cline{2-5}
& Triplet & .74 & .75 & .67 \\
\cline{2-5}
& Improved & .74 & .72 & .65 \\
\cline{2-5}
& Angular & .26 & .32 & .22 \\
\hline
\end{tabular}}}\\
\subfloat[Distance estimates after training\label{distance}]{%
{\scriptsize
\begin{tabular}{|l|l|r|r|r|r|}
\hline
Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c|}{Neg} \\
& & Mean & Std & Mean & Std \\
\hline
\multirow{4}{*}{People} & Adapted & 1.59 & 4.05 & 2.44 & 2.45 \\
\cline{2-6}
& Triplet & .46 & .18 & .55 & .10 \\
\cline{2-6}
& Improved & .15 & .38 & .21 & .18 \\
\cline{2-6}
& Angular & .51 & .25 & .06 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & 2.39 & 3.62 & 3.59 & 2.72 \\
\cline{2-6}
& Triplet & .43 & .31 & .59 & .09 \\
\cline{2-6}
& Improved & .32 & .50 & .42 & .19 \\
\cline{2-6}
& Angular & .07 & .04 & .04 & .01 \\
\hline
\end{tabular}}}
\end{wrapfigure}

@@

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.  For companies, it is from 16\% to 74\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.  Precision@1 improves from 10\% to 81\% for people and from 26\% to 75\% for companies.  In both these cases, demonstrable training occurred.

@@

\begin{wrapfigure}{r}{.4\textwidth}
\begin{center}
\caption{Precision and Recall for hard and semi-hard training}
\label{hard-semi-hard}
{\scriptsize 
\begin{tabular}{|l|r|r|r|}
\hline 
Training & Recall & Precision@1 & Precision \\
\hline 
hard & .81 & .81 & .63 \\
\hline 
semi-hard & .63 & .61 & .43 \\
\hline 
\end{tabular}}
\end{center}
\end{wrapfigure}
